Comments on Latent Ranking

### 2021-05-20 output_scripts/revisions_may.Rmd

@@

```{r ranking_sim_data}
### i&si method
count_data_dc <- get_wl_matrix(df = cbind(clean_sim_data$start,
                                          clean_sim_data$end))
isi_dc.out <- compete::isi98(m = count_data_dc, random = TRUE)
isi_dc.out$best_order

@@

agg_rank <- order(apply(agg_sims$x, 2, mean))
agg_rank

@@

gl_ranks <- order(gl_train$ratings$Rating)
gl_ranks
```

@@

Similarly, we can confirm we get sensible fits by fitting the individual
MMHP model to each pair and showing the residuals.

@@

>>>>

obj$q1 <- q1
obj$q2 <- q2

 viterbi_result <- myViterbi(events = events, 
                             param = obj,
                             termination = obs_time)

latent_inter <- interpolateLatentTrajectory(obj, 
                                            events,
                                            viterbi_result$zt_v,
                                            initial.state =
                                                 viterbi_result$initial_state,
                                            termination.time = obs_time,
                                            termination.state =
                                              viterbi_result$termination_state)

event_state <- ppdiag:::mmhp_event_state(params = obj, events = events)

latent_state <- ppdiag:::interpolate_mmhp_latent(params = obj, events,
                                                 zt = event_state$zt)

mmhp_latent <- list()
mmhp_latent$start <- 0
mmhp_latent$end <- obs_time
mmhp_latent$x <- c(0,latent_state$x.hat, obs_time)
mmhp_latent$z <- c(viterbi_result$initial_state, latent_state$z.hat)
mmhp_latent$events <- c(0, events)
mmhp_latent$zt <- c(1, event_state$zt)
ppdiag::drawUniMMHPIntensity(obj, mmhp_latent)

# this plot is not correct for later Hawkes states...

@@

```{r ranking_sim_data}
### i&si method
count_data_dc <- get_wl_matrix(df = cbind(clean_sim_data$start,
                                          clean_sim_data$end))
isi_dc.out <- compete::isi98(m = count_data_dc, random = TRUE)
as.numeric(isi_dc.out$best_order) # from highest to lowest

@@

agg_rank <- order(apply(agg_sims$x, 2, mean))
rev(agg_rank) # from highest to lowest

@@

gl_ranks <- order(gl_train$ratings$Rating)
gl_ranks #highest to lowest
```

@@

Similarly, we can confirm we get sensible fits by fitting the individual
MMHP model to each pair and showing the residuals. This
is consistent with what we see for real data, where the
residual matrices show overall small positive values, indicating
underestimation when we fit individual models.

@@

## Explaining the g function

```{r plot_g}
alpha.fun <- function(x,y,eta1,eta2)
  {
   return( eta1 * x * y *exp(-eta2 * abs(x - y) ) )
  }

f_vec <- c(0.1, 0.2, 0.4, 0.8, 0.9)

eta1 <- 6.6
eta2 <- 0.37

crossing(send = f_vec, rec = f_vec) %>% 
  filter(send != rec) %>% 
  mutate(alpha = alpha.fun(send, rec, eta1, eta2))
